---
title: "Transforming Data Frames into Time Series in R"
author: "BragatteMAS"
format: html
editor: visual
---

## Time Warp

## 1. Gather Your Data

Every journey begins with preparation. Here's our sample data frame containing daily sales:

```{r}
df <- data.frame(date = as.Date('2022-01-01') + 0:9,
                 sales = runif(10, 10, 500) + seq(50, 59)^2)
```

## 2. Choose Your Time Series Destination

R offers two primary time series classes:

-   **"ts":** Base R's classic time series object, designed for regularly spaced data.
-   **"xts":** Part of the 'xts' package, offering enhanced flexibility and features.

## 3. Embark on the Conversion Quest

**A. Transforming into "ts":**

```{r}
library(stats)  # Package for 'ts' class
# Unleash the time series magic!
ts_sales <- ts(df$sales, start = c(2022, 1), frequency = 365)  # Daily data
# Admire your creation:
print(ts_sales)
```

**Explanation:**

-   `ts()` function creates the time series object.

-   `df\$sales` specifies the data for conversion.

-   `start = c(2022, 1)` sets the starting year and month.

-   `frequency = 365` indicates daily observations (365 days per year).

**B. Shaping into "xts":**

```{r}
library(xts)  # Package for 'xts' class
# Time to shine!
xts_sales <- xts(df$sales, order.by = df$date)
# Behold your masterpiece:
print(xts_sales)
```

**Explanation:**

-   `xts()` function constructs the time series object.

-   `df\$sales` provides the data.

-   `order.by = df\$date` sets the time-based ordering.

**4. Your Time to Experiment!**

Now that you've mastered the conversion, unleash your creativity:

-   Visualize trends with plots.
-   Forecast future values.
-   Analyze patterns and seasonality.
-   Decompose time series into components.
-   And much more!


**Remember:**

-   Choose the time series class that best suits your analysis needs.
-   Always ensure your data frame has a column with valid date or time values.
-   Explore the rich functionalities of R's time series packages.

# Ref
[Unlocking the Power of Time: Transforming Data Frames into Time Series in R | R-bloggers](https://www.r-bloggers.com/2023/12/unlocking-the-power-of-time-transforming-data-frames-into-time-series-in-r/?utm_source=phpList&utm_medium=email&utm_campaign=R-bloggers-weekly&utm_content=HTML)