---
title: "outbreak.info"
author: "@#BragatteMAS"
format: html
editor: visual
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, collapse = TRUE, error = FALSE, warning = FALSE, message = FALSE)
```

# Outbreak.info

outbreak.info is a platform to discover and explore COVID-19 data and variants. Our Variant Reports allow researchers to track any emerging or known variant using customizable visualizations, enabling near real-time genomic surveillance. Our Epidemiology tools allow users to explore how COVID-19 cases and deaths are changing across locations. <https://outbreak-info.github.io/R-outbreak-info/>

## COVID Code

When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:

### Install

```{r}
# Install development version from GitHub
devtools::install_github("outbreak-info/R-outbreak-info")
```

### Auth

```{r}
outbreakinfo::authenticateUser()
```

## Genomic data

### Lineage \| Mutation Tracker

Provides access to the prevalence of a lineage, mutation(s), or lineage with additional mutations, to access the data underlying the outbreak.info Variant Tracker - in this example, mutation \[S:P681R\] (https://outbreak.info/situation-reports?muts=S%3AP681R). View the Variant Tracker Vignette to explore more options.

```{r}
library(outbreakinfo)
#  Provide GISAID credentials using authenticateUser()
# Get the prevalence of mutation P681R in the Spike protein in Kansas over time.
P681R = getPrevalence(mutations = c("S:P681R"), location = "Kansas", logInfo = FALSE)
plotPrevalenceOverTime(P681R, title = "Prevalence of S:P681R in Kansas")
```

### Location Tracker

Provides access to the prevalence of all lineages and variants in a country, state/province, or U.S. county, to access the data underlying the outbreak.info Location Tracker. View the Location Tracker Vignette to explore more options.

```{r}
library(outbreakinfo)
#  Provide GISAID credentials using authenticateUser()
# Get the prevalence of all circulating lineages in California over the past 90 days
ca_lineages = getAllLineagesByLocation(location = "California", ndays = 90)

# Plot the prevalence of the dominant lineages in California
plotAllLineagesByLocation(location =£££¡¡, ndays = 90)
```

## Tutorials

[Articles • outbreakinfo](https://outbreak-info.github.io/R-outbreak-info/articles/index.html)
