---
title: "Plots"
author: "Bragatte"
date: "18/02/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Plots 

This is a document to use easy ways to visualize and check datasets graphically.
Used Penguins dataset to change a little bit from Iris or cars.😉
<https://github.com/ttimbers/palmerpenguins>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r penguins e.g.}
install.packages("remotes")
remotes::install_github("allisonhorst/palmerpenguins")

#Data
library(palmerpenguins)
data(package = 'palmerpenguins')

#?penguins
head(penguins)
penguins_raw
str(penguins)

## Including Plots
library(tidyverse)
penguins %>%
count(species)

penguins %>%
group_by(species) %>%
summarize(across(where(is.numeric), mean, na.rm = TRUE))

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
```{r}
library(esquisse)



```



```{python}
import pandas as pd
import pandasgui as pdg


```

