---
title: "Plots"
author: "Bragatte"
date: "18|27/02/2021"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{get-started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
Git: https://github.com/BragatteMAS/R/blob/master/How_to/R2Py_Plots.Rmd
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

# Description

This is a document to use easy ways to visualize and check datasets graphically. Used Penguins dataset to change a little bit from Iris or cars.😉 <https://github.com/ttimbers/palmerpenguins>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

1.  Dataset Penguins \#R\
    1.1 Data

    1.2 Views from Data

    1.3 Clean & Prepare Data

2.  Install & call packages \#R

    2.1 Libraries

    2.2 Esquisse to interact constructing plots (base GGplotBuilder)

3.  R2Py \#R2Py

    3.1 Python packages into R

    3.2 Plot one e.g. with Seaborn library

4.  Pure Python code in R \#Python

    4.1 Py library & R Dataset

    4.2 Seaborn

## Dataset - CC (call & clean)

```{r penguins e.g.}
install.packages("remotes")
remotes::install_github("allisonhorst/palmerpenguins")

#Data
library(palmerpenguins)
data(package = 'palmerpenguins')

#?penguins
head(penguins)
penguins_raw
str(penguins)

## Including Plots
library(tidyverse)
penguins %>%
    count(species)

penguins %>%
    group_by(species) %>%
    summarize(across(where(is.numeric), mean, na.rm = TRUE))

View(penguins)

df <- penguins
```

# Plots

## R interactive plot

### Libraries

```{r setup}
library(esquisse) #R packages
```

\#\#\#Esquisse Already available at 'Addins' in RMarkdown.

```{r console esquisse}
esquisser() #Must interact - not available for knit
```

##### About esquisse:

    #esquisse(NAME OF YOUR DATAFRAME)
        Seetings for view the ggplotbuilder from esquisse
            esquisser(viewer = "browser")   open into an url - I prefer this option
            esquisser(viewer = "pane")      open into a RStudio Plot View - could BUG
                #Set display mode fix e.g.:
                    #```{r}
                    #   options("esquisse.viewer" = "browser")
                    #```

[Ref](https://github.com/dreamRs/esquisse/blob/master/vignettes/get-started.Rmd)

# R2Py

### Python packages into R

```{r}
library(reticulate) #R package to call Py libraries

#importing required Python libraries/modules
sns <- import('seaborn')
plt <- import('matplotlib.pyplot')
pd <- import('pandas')
```

### R2Py Plot one e.g.

```{r}
#building a seaborn pairplot using pairplot()
sns$pairplot(r_to_py(penguins), hue = 'species')
#display the plot
plt$show()
```

# Pure Python code in R

## Python code interactive Plot

### Py library & R Dataset

```{python}
import pandas as pd
print(r.df.head())

df_py = r.df #mark r.YOURDATA
```

### Seaborn

```{python}
import pandas as pd
import seaborn as sns
import matplotlib.pyplot as plt

sns.set_theme(style="ticks")

# Load the penguins dataset
penguins = sns.load_dataset("penguins")

# Show the joint distribution using kernel density estimation
g = sns.jointplot(
    data=penguins,
    x="bill_length_mm", y="bill_depth_mm", hue="species",
    kind="kde"
)
plt.show()
```
