---
title: "COVID_API"
author: "Bragatte"
date: "09/03/2021"
output:
  html_document: default
  pdf_document: default
info: '@Bragatte 202103091808'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# COVID API

[COVIDmap](https://covidmap.umd.edu/api.html) An open API from the University of Maryland

[Regions](https://covidmap.umd.edu/api/region) [codes_html](https://www.w3schools.com/tags/ref_urlencode.ASP)

This is an API for accessing the daily COVID-19 World Symptoms Survey data. The details of our methodology, disclaimer, and release log can be checked here. Data calculated based on the Facebook global symptoms survey data. Using the survey data, we estimate the percentage of people in a given country or region.

The base path. All URLs referenced in the documentation have the base path <https://covidmap.umd.edu/api/>

The endpoint path. For example, resources?indicator={indicator}&type={type}&country={country}&date={date}

Required parameters. These parameters must be included in a request. In the example above, {indicator}, {type}, {country}, and {date} are required. In a request, you will replace the placeholders with real values.

Optional parameters. These additional parameters can be included to customize a query to get regional aggregates, smoothed aggregates, all regions, etc.

## Packs

```{r}
packs = c("tidyverse","httr","jsonlite")
#lapply(packs, install.packages, character.only = TRUE)
lapply(packs, require, character.only = TRUE)
```

### BR

```{r}
# adding url
path <- "https://covidmap.umd.edu/api/resources?indicator=covid&type=daily&country=Brazil&daterange=20200101-20210312"

# adding url
request <- GET(url = path)

# make sure the content is encoded with 'UTF-8'
response <- content(request, as = "text", encoding = "UTF-8")

# now we can have a dataframe for use!
coviddata <- fromJSON(response, flatten = TRUE) %>% data.frame()
write.csv(coviddata,"BR_COVID.csv")
```

### BR/RS

```{r}
# adding url
path <- "https://covidmap.umd.edu/api/resources?indicator=covid&type=daily&country=Brazil&region=Rio%20Grande%20do%20Sul&daterange=20200101-20210312"

# adding url
request <- GET(url = path)

# make sure the content is encoded with 'UTF-8'
response <- content(request, as = "text", encoding = "UTF-8")

# now we can have a dataframe for use!
coviddata <- fromJSON(response, flatten = TRUE) %>% data.frame()
write.csv(coviddata,"BR_RS_COVID.csv")
```

### BR/SP

```{r}
# adding url
path <- "https://covidmap.umd.edu/api/resources?indicator=covid&type=daily&country=Brazil&region=S%C3%A3o%20Paulo"

# adding url
request <- GET(url = path)

# make sure the content is encoded with 'UTF-8'
response <- content(request, as = "text", encoding = "UTF-8")

# now we can have a dataframe for use!
coviddata <- fromJSON(response, flatten = TRUE) %>% data.frame()
write.csv(coviddata,"BR_SP_COVID.csv")
```
