---
title: "Untitled"
author: "BragatteMAS"
format: html
editor: visual
---

21 Strategies for Data Cleaning and Preprocessing in R btd Data cleaning and preprocessing in R involve various tasks, such as handling missing values, removing duplicates, transforming variables, and scaling data. Here's a list of common R codes for data cleaning and preprocessing:

1.  Handling Missing Values:

Removing rows with missing values:

```{r}
data <- na.omit(data)
Imputing missing values with mean:data$variable <-
  ifelse(is.na(data$variable),
         mean(data$variable, na.rm = TRUE),
         data$variable)
Imputing missing values with median:data$variable <-
  ifelse(is.na(data$variable),
         median(data$variable, na.rm = TRUE),
         data$variable)
```

2.  Removing Duplicates:

```{r}
Removing duplicate rows from a data frame
data <- unique(data)
Removing duplicate rows based on specific columns:data <-
  data[!duplicated(data[, c("col1", "col2")]),]
Removing duplicate columns:data <-
  data[, !duplicated(colnames(data))]
```

3.  Transforming Variables:

Log transformation:

```{r}
data$log_variable <- log(data$variable)
Square root transformation:data$sqrt_variable <- sqrt(data$variable)
Standardizing variables (mean centering and scaling):data$standardized_variable <-
  scale(data$variable)
```

4.  Encoding Categorical Variables:

Using factor for nominal variables:

```{r}
data$nominal_variable <- as.factor(data$nominal_variable)
Using model.matrix for one - hot encoding:encoded_data <-
  model.matrix( ~ ., data = data)
Converting categorical variables to numeric labels:data$cat_variable <-
  as.numeric(factor(data$cat_variable))
```

5.  Dealing with Outliers:

Identifying and removing outliers using z-scores:

```{r}
z_scores <- scale(data$variable)
outliers <- abs(z_scores) > 3
data <- data[!outliers,]
```

6.  Date and Time Manipulation: ...

# Ref

[medium_source](https://baotramduong.medium.com/data-cleaning-and-preprocessing-in-r-efb7ef6c7ce6)
